\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme{classic}
\usepackage[scale=0.82]{geometry}

% Personal data
\firstname{Nataliia}
\familyname{Rybalka}
\title{Backend Node.js Developer}
\address{Bulgaria, Sofia}{}
\mobile{+380663853677}
\mobile{+359884877793}
\email{natalirybalka21@gmail.com}
\social[github]{NataliiaRybalka}
\social[linkedin]{nataliia-rybalka-21abb2196}
%\photo[64pt][0.4pt]{images/photo}
%\social[linkedin]{...}

\definecolor{web}{rgb}{0.2,0.2,0.2}

% Content
\begin{document}

\maketitle

\section{Summary}

Backend Developer with 3 years of experience specializing in building robust, scalable, and high-performance server-side applications using Node.js. Proficient in TypeScript and JavaScript, with strong knowledge of database management systems including SQL and NoSQL. Skilled in designing and implementing RESTful APIs, optimizing application performance, and ensuring code quality through testing and best practices. Dedicated to delivering clean, maintainable code and effective solutions to complex technical challenges.

\section{Key Skills}

Programming Languages: JavaScript, TypeScript, Python\\
Frameworks \& Libraries: Express.js, NestJS, React, Redux, React Native, JWT, OAuth2, Web3, Socket.IO, Mongoose, Jest, Swagger\\
Environments: Node.js, Docker, Linux, REST APIs\\
Tools \& Platforms: Git, GitHub, Postman, Android Studio, Firebase, Webpack, Jira, VS Code, Slack\\
Cloud Platforms: AWS, Google Cloud Platform (GCP)\\
Databases: MySQL, PostgreSQL, MongoDB, AWS DynamoDB

\section{Professional Experience}

\cventry{2023 -- 2024}{Backend Node.js developer}{Vertical Change}{}{}
  {{}
   \begin{itemize}
     \item Development and supporting of CRM for Kaeser Hausverwaltung GmbH.
     \item Developing APIs in Node.js (TypeScript), including integration with third-party APIs.
     \item Reduced API response times through efficient query handling and data processing techniques.
     \item Enhanced backend scalability and maintainability.
   \end{itemize}}
\cventry{2022 -- 2023}{Backend Node.js developer}{Moonion}{}{}
  {{}
  \begin{itemize}
     \item Developed and deployed blockchain solutions, including NFTs and smart contracts, using ERC-20 and ERC-721 standards using Web3 library, ensuring secure and efficient token management on Ethereum.
     \item Supported, debugged, and enhanced the functionality of "Hangeh," a social marketplace tailored for residential buildings. Responsibilities included resolving technical issues, implementing new features, and optimizing platform performance.
     \item Writing API documentation using Swagger.
  \end{itemize}}

\section{Freelance}

\cventry{From 2023}{Backend Node.js developer}{}{}{}
  {{}
   \begin{itemize}
     \item Developed and implemented APIs in Node.js, ensuring efficient server-client interaction.
     \item Worked with third-party APIs (Google, Facebook, Microsoft, etc.), ensuring seamless integration and stable operation.
     \item Wrote unit and integration tests using Jest to ensure high code quality.
     \item Launched and maintained servers on AWS EC2, ensuring scalability and uptime.
     \item Created Android applications in React Native and Java with full server-side integration.
     \item Utilized DynamoDB, MongoDB as databases, optimizing data structures for performance.
     % \item Authored clear and structured technical documentation for ease of maintenance and future development.
   \end{itemize}}

\section{Education}

\cventry{2020 -- 2021}{JavaScript developer}
  {OktenWeb University}{Kyiv, Ukraine}{}
  {\textit{Speciality}: JavaScript Developer}
\cventry{2014 -- 2018}{Master degree}
  {Kyiv National University of Technologies and Design}{Kyiv, Ukraine}{}
  {\textit{Speciality}: Accounting}
  
\section{Pet Project}

\cventry{From 2023}{Your Best Friend Diary}{\href{https://github.com/NataliiaRybalka/diary}{\textcolor{blue}{[Link to Github]}}}{}{}
  {Mobile and Web Application with Backend{}
   \begin{itemize}
     \item Developed RESTful API using Node.js.
     \item Built the web app with React and the mobile app with React Native.
     \item Used MongoDB for data storage and management.
     \item Deployed the server on Namecheap hosting for reliable access.
     \item Delivered a cross-platform diary app with both mobile and web versions.
   \end{itemize}}

%\pagebreak

\section{Languages}

\cvdoubleitem{English}{B1}{}{}

\end{document}
